---
title: "Adjusting for Inflation"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Adjusting for Inflation}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(wealthR)
```
## Description

Adjusts a sequence of nominal financial values for inflation to reflect their real value in today's purchasing power. This function uses a monthly discount factor based on the provided annual inflation rate.The function assumes the first amount is next month. It uses the Present Value (PV) formula, specifically the Discount Factor.

## Usage
adjust_inflation(amounts, inflation_rate)

## Arguments

- `amounts`: Numeric vector. The nominal future values. The function assumes the first amount is next month.
- `inflation_rate`: Numeric. The annual inflation rate (as a decimal, e.g., 0.03 for 3%).

## Value

A numeric vector of the same length as amounts, containing values adjusted for the cumulative effect of inflation.

## Example
```{r}
nominal_values <- rep(10000, 60) # 5 years of monthly data
real_values <- adjust_inflation(nominal_values, inflation_rate = 0.03)
real_values
```
