---
title: "Adjusting for Inflation"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Adjusting for Inflation}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(wealthR)
```
## Description

Adjusts a sequence of nominal financial values for inflation to reflect their real value in today's purchasing power. This function uses a monthly discount factor based on the provided annual inflation rate.

## Usage
adjust_inflation(amounts, inflation_rate)

## Arguments

- `amounts`: Numeric vector. The nominal future values (typically the output from calc_wealth
- `inflation_rate`: Numeric. The annual inflation rate (as a decimal, e.g., 0.03 for 3%).

## Value

A numeric vector of the same length as amounts, containing values adjusted for the cumulative effect of inflation.

## Example
```{r}
# Define 'viz_data' to avoid conflict with the data() function
viz_data <- wealthR::calc_wealth(5000, 200, 0.07, 20)

plot_wealth(viz_data, title = "30-Year Real Wealth Projection")
```
