---
title: "calc_wealth"
author: "Abidur Rahman"
date: "2026-04-15"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Description

Computes the future value of an investment using a combined formula for a single lump-sum principal and a series of monthly contributions (Ordinary Annuity). It handles edge cases where the interest rate is zero to prevent calculation errors.

## Usage

```{r}
calc_wealth(principal, monthly, rate, years)
```

## Arguments

- `principal`: Numeric. Initial lump-sum investment.
- `monthly`: Numeric. Monthly contribution amount made at the end of each month.
- `rate`: Numeric. Annual nominal rate of return (as a decimal, e.g., 0.05 for 5%). Must be non-negative.
- `years`: Numeric. Total duration of the investment.

## Value

A numeric vector representing the account balance at each monthly interval throughout the specified duration.

## Example

```{r}
# Project wealth with $10,000 start, $500 monthly additions at 6% return for 30 years
wealth_trajectory <- calc_wealth(principal = 10000, monthly = 500, rate = 0.06, years = 30)
wealth_trajectory
```
