---
title: "Demo of the wealthR package"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{introduction}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```
# Overview

`wealthR` is a lightweight, zero-dependency R package for simple financial forecasting.  
It is designed to help users model investment growth, savings plans, inflation effects, and loan repayment using base R only.

The package focuses on small, practical functions that are easy to read, easy to test, and useful in real-world planning.

# What this package does

The package includes tools to:

- simulate long-term investment growth.
- adjust future values for inflation.
- project savings over time.
- forecast loan balances.
- compare multiple scenarios.
- create base R visualizations.

# Getting started


```{r setup}
library(wealthR)
```

Then you can run functions such as:

```{r raw_wealth}
# Calculate growth over 30 years
raw_wealth <- calc_wealth(principal = 10000, monthly = 500, rate = 0.07, years = 30)
head(raw_wealth,20)
```

```{r real_wealth}
# Adjust the projection for 3% annual inflation
real_wealth <-adjust_inflation(amounts = raw_wealth, inflation_rate = 0.03, years = 30)
head(real_wealth,20)
```

```{r plot_wealth}
# Compare the nominal vs. inflation-adjusted wealth
plot_wealth(raw_wealth, title = "Nominal Wealth Projection")
plot_wealth(real_wealth, title = "Inflation-Adjusted Wealth")
```
