---
title: "Introduction"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{introduction}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```
## Overview

`wealthR` is a lightweight, zero-dependency R package for simple financial forecasting.

It is designed to help users model investment growth, savings plans, and inflation effects using base R logic.

The package focuses on small, practical functions that are easy to read, easy to test, and useful for long-term financial planning.

## What this package does

The package includes tools to:

- Simulate Investment Growth: Model principal and monthly contributions with compounding interest (Ordinary Annuity).
- Adjust for Inflation: Convert future nominal values into real purchasing-power terms.
- Robust Calculations: Safely handle edge cases, such as 0 parcent interest rates or inflation.
- Base R Visualizations: Generate clean, professional wealth trajectory plots without external dependencies.

## Getting started
To begin using the package, load it into your environment:
```{r setup, include=FALSE}
library(wealthR)
```

### Calculate Nominal Growth

You can project the future value of an initial investment plus monthly contributions. The calc_wealth function calculates the balance for every month in the period.

```{r raw_wealth}
# Calculate growth over 30 years
raw_wealth <- calc_wealth(
  principal = 10000,
  monthly = 500,
  rate = 0.07,
  years = 30
)
head(raw_wealth, 12)
```
### Adjust for Inflation
To see what that money will actually buy in the future, use adjust_inflation. This function now automatically detects the time horizon based on the length of your wealth vector.
```{r real_wealth}
# Adjust the projection for 3% annual inflation
real_wealth <- adjust_inflation(
  amounts = raw_wealth,
  inflation_rate = 0.03
)
head(real_wealth, 20)
```
###Visualizing the Trajectory
The plot_wealth function provides a quick way to see the growth curve with a shaded area representing total accumulation.
```{r plot_wealth}
# Compare the nominal vs. inflation-adjusted wealth
plot_wealth(raw_wealth, title = "Nominal Wealth Projection")
plot_wealth(real_wealth, title = "Real Wealth Projection")
```
